Smart Spreading Factor Assignment for LoRaWAN

### 2018-12-30 paper.tex
interference model

\title{Paper Title*
}

@@

\par [TODO] Add LoRaWAN network architecture figure here.

@@

\par [TODO] Lowest SF suitable area section is relatively higher then the others. Most of the end devices which close to GW will fall into this area.

\par [TODO] End devices which close to the GW will probably select lowest SF all the time. Which results a lot of collisions between lowest SF transmissions while end device number close to the GW increases. Figure~\ref{fig:collision}

@@

\par Receive sensitivity of a LoRa gateway for different SFs and BWs can be found in Table \ref{table:gw_sf_sensitivity} \cite{SX1276}.

@@

\subsection{Interference Model}
[TODO]

\subsection{Simulation Assumptions}
[TODO]

@@

\section{Simulation Results} \label{Simulation Results}
[TODO] Evaluation

\section{Conclusion} \label{Conclusion}
[TODO] Summary, future works
\cite{7815384} \cite{7803607} \cite{7996384} \cite{8090518} \cite{s17061193} \cite{8267219} \cite{8430542} \cite{8319183} \cite{8480649} \cite{AN1200.22} \cite{Bor:2016:LLW:2988287.2989163} \cite{8406255} \cite{DBLP:journals/corr/abs-1802-10338} \cite{finnegan2018comparative}

\section*{Acknowledgment}
This work is supported by Turkish Ministry of Development and Istanbul Technical University researcher support program under the Grant No. ITU-AYP-2017-1.

>>>>

\title{Smart Spreading Factor Assignment for LoRaWAN
}

@@

@@

\par Initially, a node is not aware of how far it is from a GW. However, a node can guess how far away from the gateway by observing received signal power of a downlink transmission. If a downlink transmission received signal power is too high then node can decrease its next transmission SF or transmit power to decrease power consumption.
Also GW can request from a node to decrease node's SF or transmit power. This SD assignment is called lowest possible SF assignemnt scheme for the rest of the paper.

\par In Figure~\ref{fig:collision}, a LoRaWAN network distributed around a single GW is illustrated. Different color rings represent achievable range of different SF from GW and different color circles represent nodes with selected SF. Most of the end devices which close to the GW will fall into lowest SF (SF7) area section. End devices which close to the GW will probably select lowest SF all the time. Which results a lot of collisions between same SF transmissions. Collision number increases while end device number close to the GW increases.

@@

\par Receive sensitivity of a LoRa gateway for different SFs and BWs can be found in Table \ref{table:gw_sf_sensitivity} \cite{SX1276}. Maximum TX power for European ISM band LoRa default channels can be found in Table \ref{table:max_tx_power}.

@@

\begin{table}
\centering
\caption{EU863-870 ISM Band LoRa Default Channels}
\label{table:max_tx_power}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Channel} & \textbf{Frequency} & \textbf{Bandwidth} & \textbf{Max EIRP} \\ \hline
      1 &     868.1 &   125 kHz &   14 dBm \\
      2 &     868.3 &   125 kHz &   14 dBm \\
      3 &     868.5 &   125 kHz &   14 dBm \\

\hline
\end{tabular}
\end{table}

\subsection{Interference Model}
\par [TODO]

\begin{equation} \label{eq:sinr}
T = \begin{bmatrix}
       6 & -16 & -18 & -19 & -19 & -20 \\
     -24 &   6 & -20 & -22 & -22 & -22 \\
     -27 & -27 &   6 & -23 & -25 & -25 \\
     -30 & -30 & -30 &   6 & -26 & -28 \\
     -33 & -33 & -33 & -33 &   6 & -29 \\
     -36 & -36 & -36 & -36 & -36 &   6
     \end{bmatrix}
\end{equation}

\subsection{Simulation Assumptions}
\par [TODO]

@@

\section{Simulation Results} \label{Simulation Results}
\par [TODO] Evaluation

\section{Conclusion} \label{Conclusion}
\par [TODO] Summary, future works
\cite{7815384} \cite{7803607} \cite{7996384} \cite{8090518} \cite{s17061193} \cite{8267219} \cite{8430542} \cite{8319183} \cite{8480649} \cite{AN1200.22} \cite{Bor:2016:LLW:2988287.2989163} \cite{8406255} \cite{DBLP:journals/corr/abs-1802-10338} \cite{finnegan2018comparative}

\section*{Acknowledgment}
\par This work is supported by Turkish Ministry of Development and Istanbul Technical University researcher support program under the Grant No. ITU-AYP-2017-1.
